---
title: "Linear models on reconciled data"
output: html_document
date: '`r format(Sys.Date(), "%Y-%B-%d")`'
---

```{r include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(parsnip)
# See /home/share/projects/ses_multivariate.R for the code that generated the following object.
multivariate = readRDS("multivariate_reconciled.rds")

table1 =
   c(
      "CVD_mRNA",
      "diabetes_mRNA",
      "inflam1k_mRNA", "breast_cancer_mRNA",
      "Lupus_mRNA", "Colorectal_mRNA",
      "Rheumatoid_Arthritis_mRNA", "Alzheimers_mRNA",
      "Aortic_Aneurysm_mRNA", "COPD_mRNA",
      "Asthma_mRNA","Hypertension_mRNA",
      "kidney_transplant_tolerance_mRNA"
   )

summaries = c("p_univariate_parameteric_mean", "p_univariate_parameteric_median_yeo", "p_parametric")

# All because map() and kable() don't get along
dater = 
   multivariate %>%
   filter(gene_set_name %in% table1) %>% 
   filter(out_id == "result") %>% 
   unnest(out) %>% 
   filter(!str_detect(gene_set_name, "tfbm"))  %>%  
   mutate(gene_set_included = map_dbl(gene_set, length),
          cntrl_treatment = str_c(cntrl, "_", treatment)) %>% 
   select(cntrl_treatment, gene_set_name, 
          gene_set_included, all_of(summaries), ) %>% 
   unnest(all_of(summaries)) %>% 
   group_split(cntrl_treatment) %>% 
   set_names(map(., ~unlist(.x[1, 1]))) %>%  
   map(~ .x %>% 
          mutate(p_parametric_corr  = p_parametric %>% p.adjust(method = "hochberg"),
                 # p_permutation_corr  = p_permutation %>% p.adjust(method = "hochberg"),
                 p_univariate_parameteric_median_yeo_corr = p_univariate_parameteric_median_yeo %>% p.adjust(method = "hochberg"),
                 p_univariate_parameteric_mean_corr = p_univariate_parameteric_mean %>% p.adjust(method = "hochberg")#, 
                 # p_univariate_parameteric_constructed_corr = p_univariate_parameteric_constructed %>% p.adjust(method = "hochberg")
          ) %>% 
          mutate_at(vars(contains("p_")), ~ signif(., 6)))

dater %>%
   map(knitr::kable)  %>% 
   list2env(.GlobalEnv)

definitions = 
   dater %>% 
   pluck(1) %>%
   names() %>% 
   enframe(name = "variable") %>% 
   cbind(meaning = c("control and treatment", 
                     "name of signature", 
                     "number of genes included",
                     "univariate significance mean", 
                     "univariate significance median + yeo", 
                     "multivariate MANCOVA significance", 
                     # "univariate significance constructed",
                     "corrected MANCOVA p-values",
                     "corrected univariate significance median + yeo", 
                     "corrected univariate significance mean"
                     # "corrected univariate significance constructed"
   )) %>% 
   knitr::kable()


```

# Introduction

All analyses were performed with reference gene normalized data. In addition, we estimated and applied the optimal Yeo-Johnson power transformations to each gene, in order to bring each gene's distribution as close as possible to Gaussian.

# Two multivariate analyses.

Results of two linear multivariate models, treating each disease gene set as a vector. All models include the usual controls.

The p-values for parametric multivariate linear analyses derive from a Mancova style type II decomposition of the model errors, as implemented in the car::Mancova function. FDR corrections for multiplicity via Benjamini-Hochberg procedure. 

The permutation p-values for the same linear multivariate model result for permuting the focal variable - say "ses_sss_composite" - in the model's design matrix then estimating the Pillai statistic via the same procedure (car::Manova). This was repeated $N= 1000$ times creating a histogram encoding of the null distribution: i.e. the distribution of Pillai, were ses_sss_composite scores unrelated to the outcome vector. The p-value is calculated in the standard way as the fraction of the 1000 samples that were equal to, or larger than, the observed Pillai (with unpermuted predictor ses_sss_composite). Beware: pending permutations with larger $N$, some p-values were exactly 0, i.e. the observed Pillai was larger than any permutation value. In this case multiple correction is inaccurate. 

# One Univariate analysis

In lieu of treating the outcome as multivariate, we then took the median of the normalized expression values for each gene set as a scalar outcome variable. We performed standard univariate linear regression of this outcome on the same controls and treatments as above. The raw and FDR-corrected p-values for these analyses are given in each table below. 

# Notes for Wenjia

I used the median, not the mean and also applied Yeo-Johnson transforms to the univariate signatures. These, and other variations can be altered if they differ from your analysis.




# Variable names in subsequent tables

```{r}
definitions
```


# PHENOTYPE CONTROLS

```{r}
# attach(pretty)
basic_ses_sss_composite  
basic_edu_max
basic_income_hh_ff5
basic_SEI_ff5
basic_sss_5
```

# BIOLOGICAL CONTROLS

```{r}
biological_ses_sss_composite
biological_edu_max
biological_income_hh_ff5
biological_SEI_ff5
biological_sss_5
```

# BOTH BIOLOGICAL AND PHENOTYPE CONTROLS

```{r}
all_ses_sss_composite
all_edu_max
all_income_hh_ff5
all_SEI_ff5
all_sss_5
```