---
title: "2020.8.7_pca"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
ids = c("treatment", "gene_set_name", "controls")
binarize = . %>% 
  rowwise() %>% 
  mutate(across(matches("m6|m7"), ~ as.numeric(.x < 0.05))) 

```

# P-values from MANCOVA on top 9 components (m6) and the corresponding uncorrected p-values component-wise.

A note on notation: 

nn = no rotation,
vx = varimax,
ob = oblimin (oblique).

So: m6_ob is the Mancova p-value for the top 9 dimensions of oblique rotated. Collumn m7_ob_d3 is, for example, the p-value associated with dimension 3 of that outcome vector.


For ease of scanning, the second table is simply a thresholded version of the first. 1 means the uncorrected p-value is < 0.05. 0 means otherwise.

```{r, echo=FALSE}

example3 = readRDS("../rds/example3.rds")

tabPCA =
  example3 %>% 
  hoist(out, p = list("result" )) %>%
  unnest(p) %>% 
  unnest(matches("m6|m7")) %>%
  filter(names(m6_vx) == "p") %>%
  unnest(matches("m6")) %>%
  unnest_wider(m7_nn, names_sep = "_") %>% 
  unnest_wider(m7_vx, names_sep = "_") %>% 
  unnest_wider(m7_ob, names_sep = "_")

```
# No rotation

```{r}

select(tabPCA, all_of(ids), matches("nn")) %>% knitr::kable()
select(tabPCA, all_of(ids), matches("nn")) %>% binarize  %>% knitr::kable()

```

# Varimax

```{r}

select(tabPCA, all_of(ids), matches("vx")) %>% knitr::kable()
select(tabPCA, all_of(ids), matches("vx")) %>% binarize  %>% knitr::kable()

```

# Oblimin

```{r}

select(tabPCA, all_of(ids), matches("ob")) %>% knitr::kable()
select(tabPCA, all_of(ids), matches("ob")) %>% binarize  %>% knitr::kable()

```