---
title: 'tables and figures'
output: html_document
classoption: landscape
date: '`r paste("Updated on", Sys.Date())`'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,comment=NULL,message=FALSE)
library(tidyverse)
library(knitr)

```
# Table of contents
1. [table 1]
2. [PCA]

## table 1

###### FWER is a logical value, indicating if any of the P.value is less than Bonferonni threshold (0.05 / length(P.Value))?
* True means at least one P.value is less than Bonferonni threshold
* False means none of the P.value is less than Bonferonni threshold


```{r include=T,comment=NULL,message=FALSE}
readRDS("/home/xu/ses-1/user_wx/table1.rds") %>%
  kableExtra::kable(booktabs = T) %>%
  kableExtra::kable_styling()
```

## PCA

* pval_mancova: multivariate regression p value
* d1:d9: p values for each pc 

### pca non rotation

```{r include=T,comment=NULL,message=FALSE}
readRDS("/home/xu/ses-1/user_wx/pca_nn.rds") %>%
  kableExtra::kable(booktabs = T) %>%
  kableExtra::kable_styling()
```


### pca varimax rotation

```{r include=T,comment=NULL,message=FALSE}
readRDS("/home/xu/ses-1/user_wx/pca_vx.rds") %>%
  kableExtra::kable(booktabs = T) %>%
  kableExtra::kable_styling()
```

### pca oblimin rotation

```{r include=T,comment=NULL,message=FALSE}
readRDS("/home/xu/ses-1/user_wx/pca_ob.rds") %>%
  kableExtra::kable(booktabs = T) %>%
  kableExtra::kable_styling()
```